\input{header.tex}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                     % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{Current}{M.S. in Computer Science}{Columbia University}{}{}{}%{City}{\textit{Grade}}{Description}  % arguments 3 to 6 can be left empty
\cventry{2009--2013}{B.S. in Electronic Engineering}{Tsinghua University}{}{}{}%{City}{\textit{Grade}}{Description}  % arguments 3 to 6 can be left empty
%\cventry{2009}{High school}{No.2 High School attached to East China Normal University}{}{}{}%{City}{\textit{Grade}}{Description}

\section{Experience}
\subsection{Research experience}

\cvproj{Dec. 2012\\--Mar. 2013}{Greedy forwarding for mobile social networks embedded in hyperbolic spaces}{Bachelor thesis}{Supervised by Prof. Li \textsc{Su}}{EE@THU}{
\begin{itemize}
   \item Designed and evaluated a novel greedy forwarding algorithm using metrics in hyperbolic spaces;
   \item Showed that mobile social networks can be successfully embedded in such spaces, and obtains competitive performance in terms of message delivery ratio and cost;
   \item Poster presented in SIGCOMM'13.
\end{itemize}}

\cvproj{Jul. 2012\\--Sep. 2012}{Unveiling the Unique Features of Tencent(QQ) Weibo}{Research Intern}{Supervised by Prof. Jie \textsc{Tang}}{CS@THU \& Tencent}{
\begin{itemize}
\item Used Hadoop to process collected data of more than 320M users and 3.7B microblogs;
\item Studied Tencent Weibo from both macro and micro levels;
\item Discovered interesting difference between Tencent Weibo and Twitter.
\end{itemize}}

\cvproj{Aug. 2012\\--Dec. 2012}{User-level Weibo Recommendation based on Semi-Supervised Algorithm}{Research Intern}{Supervised by Prof. Jie \textsc{Tang}}{CS@THU \& Tencent}{
\begin{itemize}
\item Proposed a Factor Graph based weibo recommendation algorithm TSI-WR incorporating Social Influence with high accuracy;
\item Mainly responsible for data cleaning in the group.
\end{itemize}}

%\cventry{2011--Current}{Student Research Training Project}{Department of Computer Science}{Supervised by Prof. Baolin \textsc{Liu}}{}{
%\emph{Visual-auditory Crossmodal Effect of Elevation Recognition}
%\begin{itemize}
%\item Designed an experiment with event-related potential and behavior tests using head-related transfer function;
%\item Will complete the experiment with more than 10 subjects.
%\end{itemize}}
%\cventry{Sept. 2011--Dec. 2011}{Research intern}{Center for Quantum Information of THU}{supervised by Prof. Luming \textsc{Duan}}{}{
%\emph{Quantum Computation with Trapped Ions}
%\begin{itemize}
%\item Studied quantum information/computation theories and existing methods, did field research;
%\item Rank 3/30 in a related examination.
%\end{itemize}}
\cvproj{Feb. 2010}{Test and Evaluation of Background Extraction Algorithms}{Course Research}{}{Dept. of EE}{
\begin{itemize}
\item Realized dominant background extraction algorithms with the C++ programming language;
\item Tested speed and robustness, analyzed applicabilities of each algorithms in varied conditions.
\end{itemize}}
\cvproj{Sep. 2009\\--Oct. 2009}{An Intersection Evaluation Method Base on Pedestrians}{Course Research, Group Leader}{Supervised by Prof. Xiqin \textsc{Wang}}{}{
\begin{itemize}
\item Designed an intersection evaluation method, innovatively introduced dynamic model simulation;
\item Tested at five intersections in Beijing, proved high confidence of the method by comparing with survey results.
\end{itemize}}

\subsection{Project experience}
\cvproj{Dec 2011}{Terrain Classification Based on Locally Stationary Wavelet Model}{}{}{}{
\begin{itemize}
\item Realized locally stationary wavelet model in matlab.
\item Designed terrain classification algorithm, tested in Brodatz textures and Google Earth database with robust results.
\end{itemize}}
\cvproj{Dec 2011}{Music transcription method based on poisson point process model and beat detection}{}{}{}{
\begin{itemize}
\item Improved point process MCMC method for music transcription with beat detection based on constant Q transform.
\item Reduced the computational complexity while accuracy rate almost unchanged.
\end{itemize}}
\cvproj{May 2010}{Vocabulary-building software}{}{}{}{
\begin{itemize}
\item Application using MFC and XML, integrated Barron’s word list, GRE/TOEFL word list and Merriam-Webster Dictionary.
\item Enhance vocabulary-building speed with laws of memory.
\end{itemize}}

\section{Honors and awards}
\subsection{Contest Awards}
\cventry{2010}{Frist Prize}{Beijing Physics Contest for college students}{}{}{}
\cventry{2010}{Into the final}{Tsinghua Electronic Design Contest}{}{team leader}{}
\cventry{2010}{Rank 2\textsuperscript{nd}}{Baidu Cup Tsinghua Duishi AI Contest}{team leader}{}{}
\cventry{2010}{Rank 3\textsuperscript{rd}}{Tsinghua QuanHuang AI Contest}{}{}{}
\cventry{2009}{Frist Prize}{National Physics Contest for high school students}{}{}{\textbf{Rank 4\textsuperscript{th} all over China}}
\subsection{Scholarships}
\cventry{2010}{Samsung Scholarship}{Tsinghua University}{}{}{\textsc{cny} 3,000}
\cventry{2009}{School of Information Science and Technology Scholarship}{Tsinghua University}{}{}{\textsc{cny} 20,000}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{unsrt}
\bibliography{articles}                   % 'publications' is the name of a BibTeX file

%\section{Languages}
%\cvitemwithcomment{Language 1}{Skill level}{Comment}
%\cvitemwithcomment{Language 2}{Skill level}{Comment}
%\cvitemwithcomment{Language 3}{Skill level}{Comment}
\section{Extracurricular activities}
\cvline{Volunteer}{\small KDD2012, Beijing}
\cvline{Volunteer}{\small 28\textsuperscript{th} Challenge Cup}
\cvline{Member}{\small Tsinghua Ski Association}
\cvline{Member}{\small Tsinghua Science and Technology Association}

%\section{Standard tests}
%\cvitem{GRE}{Verbal: 155, Quantitaive: 170, Analytical Writing: 3.0}
%\cvitem{TOEFL}{Reading: 30, Listening: 30, Speaking: 22, Writing: 22}

\section{Computer skills}
\cvitem{Tools}{C/C++, R, Matlab, \LaTeX, Java, Hadoop, MySQL, verilog, Assembly}
\cvitem{Environment}{Windows, Linux}
%\cvdoubleitem{category 3}{YYY, ZZZ}{category 6}{YYY, ZZZ}

%\section{Other interests}
%\cvlistitem{Evolutionary Psychology}{}
%cvlistitem{Behavioral Economics}{}
%\cvlistitem{Photography}{}
%\cvlistitem{Alpine skiing}{}
%\section{Extra 1}r 
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem{Item 3}

%\renewcommand{\listitemsymbol}{-~}            % change the symbol for lists

%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{}

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}              % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}              % 'publications' is the name of a BibTeX file

%\clearpage\end{CJK*}                         % if you are typesetting your resume in Chinese using CJK; the \clearpage is required for fancyhdr to work correctly with CJK, though it kills the page numbering by making \lastpage undefined
\end{document}


%% end of file `resume.tex'.
