\documentclass{tccv}

\begin{document}

\part{Jingwei Zhang}

\section{Education}

\begin{yearlist}

\item[Machine Learning Track]{2013--}
     {MSc in Coumpter Science}
     {Columbia University, New York}{}{}

\item[]{2009--2013}
     {BSc in Electronic Engineering}
     {Tsinghua University, Beijing}{}{}



\end{yearlist}

\section{Working experience}

\worklist{2012}{Data Mining Intern}{Tencent(QQ) Inc.}{
\hfill\begin{tabular}{@{}p{.95\linewidth}@{}}
{\it Unveiling the Unique Features of Tencent Weibo}
\end{tabular}
{\small
\begin{itemize}
\item Used Hadoop to process collected data of more than 320M users and 3.7B microblogs;
\item Studied Tencent Weibo from both macro and micro levels, discovered interesting difference between Tencent Weibo and Twitter.
\end{itemize}}\smallskip
\hfill\begin{tabular}{@{}p{.95\linewidth}@{}}
{\it User-level Microblog Recommendation based on Semi-Supervised Algorithm}
\end{tabular}
{\small
\begin{itemize}
\item Our group proposed a Factor Graph based microblog recommendation algorithm TSI-WR (Topic-Level Social Influence based Weibo Recommendation), outperformed several baseline methods;
\item Responsible for data cleaning in the group.
\end{itemize}}}

\section{Professional experience}

\worklist{2013}{Bachelor thesis}{EE, THU}{
\hfill\begin{tabular}{@{}p{.95\linewidth}@{}}
{\it Greedy forwarding for mobile social networks embedded in hyperbolic spaces}
\end{tabular}
{\small
\begin{itemize}
\item Designed and evaluated a novel greedy message forwarding algorithm using metrics in hyperbolic spaces, obtained competitive performance in terms of message delivery ratio and cost;
\item Poster presented in SIGCOMM'13.
\end{itemize}}}

\worklist{2011}{Course project}{EE, THU}{
\hfill\begin{tabular}{@{}p{.95\linewidth}@{}}
{\it Terrain Classification Based on Wavelet Method}
\end{tabular}
{\small
\begin{itemize}
\item Used locally stationary wavelet as a feature extraction method for classifying Brodatz textures. and Google Earth data.
\end{itemize}}\smallskip
\hfill\begin{tabular}{@{}p{.95\linewidth}@{}}
{\it Music Transcription Using Gaussian Mixture Model and Beat Detection}
\end{tabular}
{\small
\begin{itemize}
\item Used beat detection (based on constant Q transform) and maximum likelihood estimation for music transcription.
\end{itemize}}}

\worklist{2010}{Course project}{EE, THU}{
\hfill\begin{tabular}{@{}p{.95\linewidth}@{}}
{\it Test and Evaluation of Background Extraction Algorithms}
\end{tabular}
{\small
\begin{itemize}
\item Implenmented some background extraction algorithms using C++, analyzed the applicabilities of each algorithm in varied conditions.
\end{itemize}}\smallskip
\hfill\begin{tabular}{@{}p{.95\linewidth}@{}}
{\it Vocabulary-building software}
\end{tabular}
{\small
\begin{itemize}
\item Designed an application using MFC and XML, integrated multiple words lists and dictionaries, aims to enhance memorization speed.
\end{itemize}}}

\personal[iceboal.com]{157 W 106th St Apt 3D}{New York, NY 10025}{+1 (347) 821-1086}{iceboal@gmail.com}

\section{Contest}

\begin{yearlist}

\item{2013}{Rank 18\textsuperscript{th}}{Kaggle Contest: Multi-label Bird Species Classification - NIPS 2013}{Kaggle.com rank: 964\textsuperscript{th} / 136,948 users}{}

\item{2010}{Rank 2\textsuperscript{nd}}{Baidu Cup Tsinghua Duishi AI Contest}{}{team leader}

\item{2010}{Rank 3\textsuperscript{rd}}{Tsinghua QuanHuang AI Contest}{}{}

\item{2009}{Rank 4\textsuperscript{th} / $\sim$ 500,000 students}{National Physics Contest for high school students in China}{}{}



\end{yearlist}

\section{Scholarships}

\begin{yearlist}

\item{2010}{Samsung Scholarship}{Tsinghua University}{}{\textsc{cny} 3,000}
\item{2009}{School of Information Sci. and Tech. Scholarship}{Tsinghua University}{}{\textsc{cny} 20,000}


\end{yearlist}

\section{Publications}

\textbf{Jingwei Zhang}.
\emph{Greedy forwarding for mobile social networks embedded in hyperbolic spaces}.
\emph{SIGCOMM 2013}: 555--556, poster.\medskip

Daifeng Li, \textbf{Jingwei Zhang}, Golden Guo-zheng Sun, Jie Tang, Ying
Ding and Zhipeng Luo.
\emph{What is the Nature of Chinese MicroBlogging: Unveiling the Unique Features of Tencent Weibo}.
arXiv:1211.2197.\medskip

\section{Skills}

\begin{factlist}

\item{Good Level}
      {R, C++, Matlab, Python, Hadoop, \LaTeX, Vim}

\item{Basic Level}
      {Java, MySQL, Linux, Shell script}

\end{factlist}

\end{document}